---
title: "My Web Scraping Exercise"
author: "John Karuitha"
date: "5/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE, include=FALSE)

library(tidyverse)
library(rvest)
library(htmltools)
tagList(rmarkdown::html_dependency_font_awesome())
```

# Web Scraping Exercises

In this website, there are names that span over 20 pages. Each page displays 50 names. The exercise is to scrap all the 20 pages. 

```{r}
results <- read_html("http://www.vondel.humanities.uva.nl/ecartico/persons/index.php?subtask=browse")

results_scrap <- results %>% 
  
  html_nodes("#setwidth li a") %>% 
  
  html_text()
```

## Get the Attributes 
These attributes are the web addresses of the 20 pages. 

```{r}
results_attr <- results %>% 
  
  html_nodes("#setwidth li a") %>% 
  
  html_attrs()
```


## Table of Names and Attributes
This tibble consists of the 50 names and the 50 relative urls. 

```{r}
results_df <- tibble(results_scrap, results_attr)
```

## Updating the URLs
These are the weblinks for the first 50 names. 

```{r}
results_to_crawl <- results_df %>% 
  
  mutate(full_url = glue::glue("http://www.vondel.humanities.uva.nl{results_attr}")) %>% 
  
  select(full_url)
```

## Crawling the rest of the navigation

```{r}
#######################################
navigation <- results %>% 
  
  html_nodes("form+ .subnav a") %>% 
  
  html_attrs()

navigation_tibble <- tibble(navigation)

#######################################
navigation_tibble
```

